Stability in human interaction networks: primitive typology of vertex, prominence of measures and activity statistics

### 2015-01-21 paper.tex
arrumado caption das figuras finais

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/5000}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp5000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/5000_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp5000_}
\end{figure*}

%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/1000}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp1000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/1000_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp1000_}
\end{figure*}

%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/500}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp500}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/500_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp500_}
\end{figure*}

%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/250}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp250}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/250_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp250_}
\end{figure*}

%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/100}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp100}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/100_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp100_}
\end{figure*}

%%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/50}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp50}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/50_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp50_}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/10000}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad10000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/10000_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad10000_}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/5000}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad5000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/5000_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad5000_}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/1000}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad1000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/1000_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad1000_}
\end{figure*}

%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/500}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad500}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/500_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad500_}
\end{figure*}

%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/250}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad250}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/250_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad250_}
\end{figure*}

%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/100}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad100}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/100_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad100_}
\end{figure*}

%%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/50}
    \caption{Distribution of vertex with respect to each measure of activity: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad50}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/50_2}
    \caption{Distribution of vertex with respect to each measure of activity: compound criteria. Red, green and blue are for hubs, intermediary and border (peripheral) vertex fractions. The first two plots picture classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black is used to depict how much a vertex was classified in more than section: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad50_}
\end{figure*}

>>>>

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/5000}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp5000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/5000_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp5000_}
\end{figure*}

%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/1000}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp1000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/1000_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp1000_}
\end{figure*}

%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/500}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp500}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/500_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp500_}
\end{figure*}

%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/250}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp250}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/250_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp250_}
\end{figure*}

%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/100}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp100}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/100_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp100_}
\end{figure*}

%%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/50}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. CPP Std library official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:cpp50}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/CPP/50_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:cpp50_}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/10000}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad10000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/10000_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad10000_}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/5000}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad5000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/5000_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad5000_}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/1000}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad1000}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/1000_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad1000_}
\end{figure*}

%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/500}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad500}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/500_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad500_}
\end{figure*}

%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/250}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad250}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/250_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad250_}
\end{figure*}

%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/100}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad100}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/100_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad100_}
\end{figure*}

%%%%%%%%%%
\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/50}
    \caption{Distribution of vertexes with respect to each centrality measure: in and out degrees and strengths. Linux Audio Users (LAD) official mailing list. In the first six plots, red is fraction of hubs, green is the fraction of intermediary and blue is for peripheral fraction. On the last plot, red is the center (maximum distance to another vertex is equal to radius), blue is periphery (maximum distance equals to diameter) of the giant component. On the same graph, green counts the disconnected vertexes.}
    \label{fig:lad50}
\end{figure*}

\begin{figure*}[hbtp] 
   \centering
        \includegraphics[width=\textwidth]{figs/LAD/50_2}
    \caption{Distribution of vertex with respect to compound criteria. Red, green and blue designate hubs, intermediary and border (peripheral) vertex fractions. The first two plots exhibit classifications that are not functions. Thus, in the first plot, the fraction of vertexes with unique classification in plotted in black. On the second plot, black represents the fraction of vertexes that has more than one class: $\frac{\text{number of classifications} - \text{number of nodes}}{\text{number of nodes}}$. Compound criteria is described in Section~\ref{sectioning}.}
    \label{fig:lad50_}
\end{figure*}
